% ── Abstract (English) ───────────────────────────────────────

\noindent
The growing demand for intelligent health monitoring in Ambient Assisted Living
(AAL) environments renders Human Activity Recognition (HAR) a critical research
domain. Classical centralized machine learning approaches require the transfer
of sensitive mobile sensor data to central servers, raising serious concerns
about user privacy.

This thesis proposes a Federated Learning (FL) system for HAR in AAL
environments, which preserves data locally on each device and transmits only
model parameter updates to the central server. A fundamental limitation of
existing FL systems is the absence of mechanisms that incentivize rational users
to actively participate and contribute high-quality data. To address this
shortcoming, an incentive mechanism based on Stackelberg Game Theory is designed
and implemented, in which the central server acts as the leader by determining
the reward structure, while the clients act as followers optimizing their level
of effort.

Furthermore, to evaluate the contribution of each participating client, a system
based on Shapley Values from Cooperative Game Theory is developed, ensuring fair
reward allocation proportional to each client's marginal contribution to the
global model's recognition capability. The proposed architecture is implemented
using a one-dimensional Convolutional Neural Network (1D-CNN) specifically
designed for sensor time-series analysis, with the federated training protocol
(FedAvg) implemented from scratch in PyTorch.

Evaluation is conducted on two datasets: the established UCI Human Activity
Recognition dataset under controlled conditions, and the AAL Smartphone
Dataset for HAR in AAL under real-world conditions with heterogeneous,
Non-IID data distributions across 22 user-clients. Initial evaluation confirms
the system is functional: a federated accuracy of $76.8\%$ versus $84.8\%$ for
centralized training quantifies the cost of Non-IID heterogeneity. The
quantitative comparison of contribution metrics (Leave-One-Out versus Shapley)
for finalizing the incentive mechanism constitutes the next stage of this work.

\vspace{1.5em}
\noindent
\textbf{Keywords:}
Federated Learning,
Human Activity Recognition (HAR),
Ambient Assisted Living (AAL),
Digital Twin,
Game Theory,
Stackelberg Game,
Shapley Values,
Incentive Mechanisms.
